Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-04-07 Writing/manuscript_cea.rmd
minor changes in text

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield levels most accurately at the observed points, and the following step used the selected model to predict EONR. As discussed earlier, this practice can be economically harmful. Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem. It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds. As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation round 20 and 30).

@@

Table \@ref(tab:count-table) summarizes the relationship between yield and EONR prediction RMSE for all the simulation rounds. It shows clearly that following the process would lead to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds, the RF model performed the best at yield prediction among RF, BRF, and CNN, but did not provide EONR estimates that led to the highest profit. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, the two-step process worked well. For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.

>>>>

All previous research has followed a two-step procedure to estimate site-specific EONRs. The first step was to select the model that predicts yield levels most accurately at the observed points, and the following step used the selected model to predict EONR. As discussed earlier, this practice can be economically harmful. Figure \@ref(fig:vis-RMSE-y-eonr) further illustrates the underlying problem. It plots RMSE of yield (x-axis) and EONR (y-axis) predictions by model and simulation round for several simulation rounds. As you can see clearly, the model with the lowest yield RMSE is not necessarily the model with the lower EONR RMSE for a given simulation round (simulation rounds 10, 20, and 30).

@@

Table \@ref(tab:count-table) summarizes the relationship between yield and EONR prediction RMSE for all the simulation rounds. It shows clearly that following the process would lead to the choice of the best (as measured by profit) EONR prediction model in fewer than $30\%$ of the "aby" and "abytt" simulation rounds, $40\%$ of the "aabbyy" simulation rounds, and $50\%$ of the "aabbyytt" simulation rounds. For example, the table shows that, in the "aby" scenario, RF attained the lowest RMSE for yield prediction in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` of 1000 iterations, and attained the lowest $\hat{\pi}_{def}$ in `r summary_res_CNN_RF_BRF[Model=="aby", count_RF]` of those `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` iterations. That is, in `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]-summary_res_CNN_RF_BRF[Model=="aby", count_RF]` out of `r summary_res_CNN_RF_BRF[Model=="aby", count_y_RF]` rounds where the RF model performed the best at yield prediction among RF, BRF, and CNN,RF did not provide EONR estimates that led to the highest profit. Similarly, in no case did the CNN method provide both the best yield prediction and the best EONR estimation simultaneously. In the rounds in which BRF predicted yield best, the two-step process worked well. For example, Table \@ref(tab:count-table) shows that BRF predicted EONR best in `r summary_res_CNN_RF_BRF[Model=="aby", count_BRF]` of the `r summary_res_CNN_RF_BRF[Model=="aby", count_y_BRF]` "aby" simulation rounds in which it predicted yields best. But BRF predicted yields best in fewer than $30\%$ of the rounds, implying that the two-step procedure failed more than $70\%$ of the time.
